## This is my assingment 1 markdown file.
=========================================

Load activity data.

```{r}
data<-read.csv("activity.csv",header=TRUE)
library(dplyr)
datatmp<-tbl_df(data)
```

Analysis 1 

```{r}
data1<-filter(datatmp,!is.na(steps))
by_date<-group_by(data1,date)
res1<-summarize(by_date,steps=sum(steps))
hist(res1$steps)
by_date_mean<-summarize(res1,mean=mean(steps))
by_date_median<-summarize(res1,median=median(steps))

```

Mean toltal number of steps taken per day is `r by_date_mean`.
Median total numer of steps taken per day is `r by_date_median`.


Analysis 2

```{r}
by_interval<-group_by(data1,interval)
res2<-summarize(by_interval,act=mean(steps))
res2_max<-max(res2$act)
plot(res2$interval,res2$act,"l")
Inteval_max<-filter(res2,act==max(act))[1,1]
```
`Interval_max` has the max numerber of on average across all the days in the dataset, contains the maximum number of steps.

Analysis 3

```{r}
datafill<-datatmp
for(i in 1:nrow(data)){
        if(is.na(data[i,1])==TRUE){
                datafill[i,1]=filter(res2,interval==data[i,3])[1,2] 
        }   
}
datafill_by_date<-group_by(datafill,date)
res1_fill<-summarize(datafill_by_date,steps=sum(steps))
hist(res1_fill$steps)

res1_fill_mean<-summarize(res1_fill,mean=mean(steps))
res1_fill_median<-summarize(res1_fill,median=median(steps))

datafill_by_interval<-group_by(data1,interval)
res2_fill<-summarize(by_interval,act=mean(steps))
plot(res2_fill$interval,res2$act,"l")
```

Mean toltal number of steps taken per day using fill in data set is `r by_date_mean`.
Median total numer of steps taken per day is using fill in data set `r by_date_median`.
They are almost have no difference because we use the mean for that 5-minute interval.

Analysis 4

```{r}
datafillweek<-datafill
datafillweek$date<-as.factor(weekdays(as.Date(datafillweek$date)))

levels(datafillweek$date)[levels(datafillweek$date)%in%c("星期六" ,"星期日")]<-"weekend"
levels(datafillweek$date)[levels(datafillweek$date)%in%c( "星期二","星期三","星期四","星期五","星期一")]<-"weekday"

res4_weekdaytmp<-filter(datafillweek,date=="weekday")
res4_weekendtmp<-filter(datafillweek,date=="weekend")
by_interval_weekday<-group_by(res4_weekdaytmp,interval)
by_interval_weekend<-group_by(res4_weekendtmp,interval)
res4_weekday<-summarize(by_interval_weekday,act=mean(steps))
res4_weekend<-summarize(by_interval_weekend,act=mean(steps))
par(mfrow = c(1, 2))
plot(res4_weekday$interval,res2$act,"l")
plot(res4_weekend$interval,res2$act,"l")
```

The weekday and weekend data are slightly different.

